Astro 507; Problem Set 4

### 2022-03-09 pset4/solutions.tex
progress on question 2
setup rest of the questions
pset4 2a added

>>>>

\question{\textbf{Water/Ice Mass-Radius Relation}}

\question{2a. \textbf{Sketch}}
\answer{
    I struggled with sketching this so I instead just plotted the functions directly. In the plot below, the blue curve shows the approximate equation of state which is given by
    \begin{equation}
        \rho(P) = \rho_0 + K P^{n}
    \end{equation}
    The orange curve is in the regime in which $P$ is very large and so we can assume that the first term can be neglected such that
    \begin{equation}
        \rho(P) = K P^n
    \end{equation}
    Rearranging this into a polytrope form gives
    \begin{equation}
        \boxed{ P(\rho) = \qty(\frac{\rho}{K})^{1/n} } 
    \end{equation}
    and so the adiabatic index in this case is $\Gamma = 1 / n$. Since $n = 0.513$, this means that the water is stiffer than an adiabatic ideal gas at high pressure since $\Gamma = 1 / 0.513 = 1.95$ is larger than $5/3$.
    \begin{center}
        \includegraphics[width=\textwidth]{figures/2a.pdf}
    \end{center}
}

\question{2b. \textbf{Transition pressure}}
\answer{

}

\question{2c. \textbf{Temperature Assumptions}}
\answer{

}

\question{2d. \textbf{Maximum Mass}}
\answer{

}

\question{\textbf{Radiation-dominated star}}

\question{3a. \textbf{Temperature expression}}
\answer{
    See notebook but $1/n$ and so stiffer.
}

\question{3b. \textbf{Lower-limit on mass}}
\answer{

}

\question{3c. \textbf{Evaluate mass}}
\answer{

}

\question{3d. \textbf{Polytropes}}
\answer{

}

\question{3e. \textbf{Lane-Emden equation}}
\answer{

}
